Trans-Dimensional Bayesian Inference for Gravitational Lens Substructures

### 2015-09-10 Papers/ms.tex
More number updates

Despite weak evidence for the existence of substructure, when we examine the
expected value of the empirical measure of substructure positions
(Figure~\ref{fig:substructures3}) we find no consistency in their positions,
unlike for the simulated data (Figure~\ref{fig:substructures1}). This situation
is not uncommon. For example, \citet{exoplanet} found evidence for a large
number of Keplerian signals in a time series, but the number of such signals
with well constrained properties was much lower. Related to this, we can
compute posterior probabilities for any hypothesis about the substructure
masses. With 95\% probability the substructure mass is less than 5.80$\times 10^{12}$ solar masses and with 75\% probability it is less than 3.56$\times 10^{12}$ solar masses. As the Einstein ring itself implies a mass of about $5 \times 10^{12}$
solar masses, these summaries are affected by the possibility of blobs outside
the main Einstein ring.

>>>>

Despite weak evidence for the existence of substructure, when we examine the
expected value of the empirical measure of substructure positions
(Figure~\ref{fig:substructures3}) we find no consistency in their positions,
unlike for the simulated data (Figure~\ref{fig:substructures1}). This situation
is not uncommon. For example, \citet{exoplanet} found evidence for a large
number of Keplerian signals in a time series, but the number of such signals
with well constrained properties was much lower. Related to this, we can
compute posterior probabilities for any hypothesis about the substructure
masses. With 95\% probability the substructure mass is less than {\revisions 1.53$\times 10^{13}$} solar masses and with 75\% probability it is less than {\revisions 5.10$\times 10^{12}$} solar masses. As the Einstein ring itself implies a mass of about $5 \times 10^{12}$
solar masses, these summaries are affected by the possibility of blobs outside
the main Einstein ring.
